PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-13 paper/ms.tex
manuscript: fix column width

The 2-minute stacks for \ptfo\ were reduced to light curves by the
Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
Conditioning (PDC) light curve.  The PDC light curve aperture used
pixels chosen to maximize the SNR of the total flux of the target
\citep{bryson_2020_target_aperture}.  Non-astrophysical variability
was removed by fitting out trends common to many stars
\citep{smith_kepler_2012,stumpe_multiscale_2014}.
% \citep{smith_kepler_PDC_2017}
% \citep{smith_kepler_apertures_2017}

>>>>

The 2-minute stacks for \ptfo\ were reduced to light curves by the
Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
Conditioning Simple Aperture Photometry (PDCSAP) light curve.  The PDC
light curve aperture used pixels chosen to maximize the SNR of the
total flux of the target \citep{bryson_2020_target_aperture}.
Non-astrophysical variability was removed by fitting out trends common
to many stars \citep{smith_kepler_2012,stumpe_multiscale_2014}.
